---
title: "AirbnbReport"
author: "Shiksha Mann"
date: "6 February 2016"
output: html_document
---

Airbnb Booking Analysis
==========================================

**BDA** - *INSEAD MBA 16J*


 
## Business motivation



<br>


## Data Description
 
First, let's look at the data

```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
local_directory=getwd()
source(paste(local_directory,"/R/library.R",sep="/"))
airbnbdata= within(read.csv(paste(local_directory,"/data/Airbnb_data1.csv",sep="/")),rm("X"))
library(googleVis)
t1 <- gvisTable(airbnbdata[,],options = list(showRowNumber = FALSE, width = 800, height = min(400,27*(nrow(airbnbdata) + 1)), allowHTML = TRUE, page = 'disable'))
print(t1,'chart')
```

It is very important to understand the columns, let's review its content:

* **id_visitor**: the id of the visitor
* **id_session**: the id of the session
* **dim_session_number**: the number of session on a given day for a visitor
* **dim_user_agent**: the user agent of the session
* **dim_device_app_combo**: the parsed out device/app combo from user agent
* **ds**: date stamp of session
* **ts_min**: time of session start
* **ts_max**: time of session end
* **did_search**: binary flag indicating if the visitor performed a search during the session
* **sent_message**: binary flag indicating if the visitor sent a message during the session
* **sent_booking_request**: binary flag indicating if the visitor sent a booking request during the session

## Introductory analysis


##
Number of visits per booking
```{r echo=TRUE, eval=TRUE, tidy=TRUE}
airbnb_visits = nrow(airbnbdata)
class(airbnbdata)
airbnb_bookings = sum(as.numeric(airbnbdata[11,]))
Visit_per_booking = airbnb_visits/airbnb_bookings

```

For Looking at Desktop bookings with Chrome

```{r echo=TRUE, eval=TRUE, tidy=TRUE}
airbnb_visits_Chrome = airbnbdata[airbnbdata$dim_device_app_combo =="Desktop - Chrome", ]
airbnb_visits_Chrome = nrow(airbnb_visits_Chrome)-1
airbnb_bookings_Chrome = sum(airbnb_visits_Chrome[11,])
Visit_per_booking_Chrome = airbnb_visits_Chrome/airbnb_bookings_Chrome
```

#airbnb_bookings <-  group_by(airbnb_visits, factor(source)) %>% #summarise(sent_booking_request = sum(sent_booking_request))
#airbnb_bookings = data.frame(pages = airbnb_bookings$`factor(source)`, sent_booking_request = airbnb_bookings$sent_booking_request)
airbnb_bookings = airbnb_bookings[sort(airbnb_bookings$sent_booking_request, decreasing =  TRUE, index.return = TRUE)$ix,]

gadata_referral = gadata[gadata$Medium =="referral", ]
source_referral <-  group_by(gadata_referral, factor(source)) %>% summarise(pageviews = sum(pageviews))
source_referral = data.frame(pages = source_referral$`factor(source)`, pageviews = source_referral$pageviews)
source_referral = source_referral[sort(source_referral$pageviews, decreasing =  TRUE, index.return = TRUE)$ix,]
#```

#```{r echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
show_data = data.frame(source_referral)
m1<-gvisTable(show_data,options=list(showRowNumber=TRUE,width=1220, height=min(400,27*(nrow(show_data)+1)),allowHTML=TRUE,page='disable'))
print(m1,'chart')
```
